\documentclass[12pt]{exam}
\usepackage[utf8]{inputenc}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage{multicol}
\usepackage{listings}

\newcommand{\class}{Advanced Computer Architecture }
\newcommand{\term}{Summer 2017}
\newcommand{\examnum}{Exam 3}
\newcommand{\examdate}{07/21/2017}
\newcommand{\timelimit}{07/25/2017}
%\newcommand{\numquestions}{5}
%\newcommand{\numpoints}{100}
%\newcommand{\numpages}{2}

\pagestyle{head}
\firstpageheader{}{}{}
\runningheader{\class}{\examnum\ - Page \thepage\ of \numpages}{\examdate}
\runningheadrule


\begin{document}

\noindent
\begin{tabular*}{\textwidth}{l @{\extracolsep{\fill}} r @{\extracolsep{6pt}} l}
\textbf{\term} &&\\
\textbf{\examnum} &&\\
\textbf{\examdate} &&\\
\end{tabular*}\\
\rule[2ex]{\textwidth}{2pt}

This exam contains \numpages\ pages (including this cover page) and \numquestions\ questions.\\

\textbf{Instructions}
\begin{enumerate}
\item \textit{Read every question very carefully.}
\item \textit{You should be able to finish this exam in an hour.}
\item \textit{For descriptive questions, please complete the answer in 5-10 sentences.}
\item \textit{Please try to submit soft copies. If you are planning to submit scanned copies of hand-written answers, please make sure they are very clear.}
\item \textit{Please join all the scanned copies or images to one PDF file and upload that final file to D2L.}
\item \textit{Total points for the exam is \numpoints.}
\item \textit{\bf{Late submissions minus 10 points.}}
\end{enumerate}

\begin{center}
Grade Table (for teacher use only)\\
\addpoints
\gradetable[v][questions]
\end{center}

\noindent
\rule[2ex]{\textwidth}{2pt}

\newpage
\begin{questions}

\question[20] Explain the skeleton of a simple GPU program (assume the program is a simple vector addtion).  
\addpoints

\question[20] 
Explain the following:
\noaddpoints % to omit double points count
\begin{parts}
\part[10] ACID properties
\part[10] CAP theorem 
\end{parts}
\addpoints


\question [20] 
Explain the following terms in the context of Internet
\noaddpoints 
\begin{parts}
\part[5] IP address
\part[5] Application protocol
\part[5] Transmission Control Protocol (TCP)
\part[5] Internet Protocol (IP)
\end{parts}
\addpoints


\question[20] From the Table 1, Which computer (System A or System B) will you buy (assume they have the same price) and give reasons for your decision.
\addpoints
\begin{table}[h]
\centering
\label{tbl}
\begin{tabular}{l|l|l|l}
 Program& Execution frequency &  Execution time (A) & Execution time (B)  \\\hline \hline
 Vector addition & 50\% & 50 & 50   \\
 Matrix multiplication&   30\%  & 250  & 300  \\
 Matrix transpose & 20\% & 100 & 80 \\\hline 
\end{tabular}
\caption{Benchmark program execution time comparison of System A and System B}
\end{table}

\question[20] Name and explain the four different approaches of CPU scheduling.  
\addpoints

\end{questions}

\end{document}

