\documentclass[12pt]{exam}
\usepackage[utf8]{inputenc}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage{multicol}
\usepackage{listings}

\newcommand{\class}{Advanced Computer Architecture }
\newcommand{\term}{Summer 2017}
\newcommand{\examnum}{Exam 1}
\newcommand{\examdate}{06/20/2017}
\newcommand{\timelimit}{1 day}
%\newcommand{\numquestions}{5}
%\newcommand{\numpoints}{100}
%\newcommand{\numpages}{2}

\pagestyle{head}
\firstpageheader{}{}{}
\runningheader{\class}{\examnum\ - Page \thepage\ of \numpages}{\examdate}
\runningheadrule


\begin{document}

\noindent
\begin{tabular*}{\textwidth}{l @{\extracolsep{\fill}} r @{\extracolsep{6pt}} l}
\textbf{\term} &&\\
\textbf{\examnum} &&\\
\textbf{\examdate} &&\\
\end{tabular*}\\
\rule[2ex]{\textwidth}{2pt}

This exam contains \numpages\ pages (including this cover page) and \numquestions\ questions.\\

\textbf{Instructions}
\begin{enumerate}
\item \textit{Read every question very carefully.}
\item \textit{You should be able to finish this exam in an hour.}
\item \textit{For descriptive questions, please complete the answer in 5-10 sentences.}
\item \textit{Please try to submit soft copies. If you are planning to submit scanned copies of hand-written answers, please make sure they are very clear.}
\item \textit{Total points for the exam is \numpoints.}
\end{enumerate}

\begin{center}
Grade Table (for teacher use only)\\
\addpoints
\gradetable[v][questions]
\end{center}

\noindent
\rule[2ex]{\textwidth}{2pt}

\newpage
\begin{questions}

\question[20] Explain the von Neumann architecture with a clear diagram.
\addpoints

\question[20] Explain how the set associative cache scheme combine the advantages of direct mapped cache and fully associative cache.
\addpoints

\question [20] Perform the following operations.
\noaddpoints % to omit double points count
\begin{parts}
\part[5] Convert $1234$ to binary
\part[5] Convert $1011010_2$ to decimal
\part[5] Convert $1010101010101010_2$ to hexadecimal
\part[5] Convert $101101101101_2$ to octal
\end{parts}
\addpoints


\question [20] What are the DECIMAL values of the following registers in a MARIE computer after executing the selected line in the code given below.
\noaddpoints % to omit double points count
\begin{lstlisting}
Load	X 
Add	Y 
Store 	Z /AFTER EXECUTING THIS LINE 
Halt
X,	Dec	1
Y,	Dec	2
Z,	Hex 	111
\end{lstlisting}
\begin{parts}
\part[5] AC
\part[5] IR
\part[5] PC
\part[5] MBR
\end{parts}
\addpoints

\question [20] Describe some of the challenges in designing an ISA.
\end{questions}

\end{document}

