\documentclass[12pt]{exam}
\usepackage[utf8]{inputenc}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage{multicol}
\usepackage{listings}

\newcommand{\class}{Advanced Computer Architecture }
\newcommand{\term}{Summer 2017}
\newcommand{\examnum}{Exam 2}
\newcommand{\examdate}{07/06/2017}
\newcommand{\timelimit}{1 day}
%\newcommand{\numquestions}{5}
%\newcommand{\numpoints}{100}
%\newcommand{\numpages}{2}

\pagestyle{head}
\firstpageheader{}{}{}
\runningheader{\class}{\examnum\ - Page \thepage\ of \numpages}{\examdate}
\runningheadrule


\begin{document}

\noindent
\begin{tabular*}{\textwidth}{l @{\extracolsep{\fill}} r @{\extracolsep{6pt}} l}
\textbf{\term} &&\\
\textbf{\examnum} &&\\
\textbf{\examdate} &&\\
\end{tabular*}\\
\rule[2ex]{\textwidth}{2pt}

This exam contains \numpages\ pages (including this cover page) and \numquestions\ questions.\\

\textbf{Instructions}
\begin{enumerate}
\item \textit{Read every question very carefully.}
\item \textit{You should be able to finish this exam in an hour.}
\item \textit{For descriptive questions, please complete the answer in 5-10 sentences.}
\item \textit{Please try to submit soft copies. If you are planning to submit scanned copies of hand-written answers, please make sure they are very clear.}
\item \textit{Please join all the scanned copies or images to one PDF file and upload that final file to D2L.}
\item \textit{Total points for the exam is \numpoints.}
\item \textit{\bf{Late submissions minus 10 points.}}
\end{enumerate}

\begin{center}
Grade Table (for teacher use only)\\
\addpoints
\gradetable[v][questions]
\end{center}

\noindent
\rule[2ex]{\textwidth}{2pt}

\newpage
\begin{questions}

\question[20] Explain the terms throughput and latency. 
\addpoints

\question[20] 
Explain using Amdahl's Law  how we can possibly improve the overall performance of a computer  cheaper by buying better memory than buying better processor. 
\addpoints

\question [20] Explain the step-by-step diagram of the following actions in a RAID Level 5 (assume there are only 3 discs). 
\noaddpoints % to omit double points count
\begin{parts}
\part[10] How data is added to the discs?
\part[10] How the data is recovered in case of a disc failure? 
\end{parts}
\addpoints


\question [20] 
Describe the six phases of a compiler in translating a computer language to a machine language. 
\addpoints

\question [5] Draw example architecture diagrams for the following systems.
\noaddpoints 
\begin{parts}
\part[5] SMP, Symmetric multiprocessors
\part[5] MPP, Massively parallel processors
\part[5] Hybrid of MPP and SMP
\part[5] Extended Flynn's taxonomy.
\end{parts}
\addpoints
\end{questions}

\end{document}

